Percolation Analysis – Building a Package

### 2019-07-31 paper.Rmd
nodes_clust und map_clust funktionieren. hänge bei cluster_freq

percolate2(data = data, radius_values = 10, limit = 500, radius_unit = 1)

source("R/mapping_clusters.v4.12.R")
mapClusters(data = data, radius_values = 10, limit = 500, radius_unit = 1, upper_radius = 200, lower_radius = 20, step_value = 20, shape = sNL_shape)

>>>>

percolate2(data = data, radius_values = 10, limit = 500, radius_unit = 1, upper_radius = 200, lower_radius = 20, step_value = 20)

source("R/mapping_clusters.v4.12.R")
mapClusters(data = data, radius_values = 10, limit = 500, radius_unit = 1, upper_radius = 200, lower_radius = 20, step_value = 20, shape = sNL_shape, map_name = "sNL-Karte")
